Semistochastic importance sampling of second-quantized operators in determinant space

### 2021-06-04 notes/talk/talk.tex
Small changes

\section{Algorithm}
\subsection{Deterministic component}
\begin{frame}{Deterministic component}
	\Wider{
		\begin{itemize}
			\item  \textbf{Setup:}
			\begin{itemize}
				\item  For each pair of orbitals $\left\{p,q\right\}$, store a list of %triplets
				$\left\{r,s,\left|H\left(rs\leftarrow pq\right)\right|\right\}$,
				sorted by $\left|H\left(rs\leftarrow pq\right)\right|$ in decreasing order
			\end{itemize}
			{\color{white}  skip line}
			\\
			\uncover<2->{
				\item \textbf{Finding important connected determinants} $D_j$ (for which $\left|H_{ji}\right|>\epsilon$): %for at least one $i\in \mathcal{V}$)
				\\{\color{white}  skip line}
				\\
			}
			\begin{itemize}
				\uncover<3->{
					\item  \textbf{Generate only those double excitations that exceed $\epsilon$.}
					\\For each pair of occupied orbitals $\left\{p,q\right\}$, look up the stored list
					of triplets $\left\{r,s,\left|H\left(rs\leftarrow pq\right)\right|\right\}$ and iterate
					through the list until a triplet is reached for which $\left|H\left(rs\leftarrow pq\right)\right|<\epsilon$
				}
				\\{\color{white}  skip line}
				\\
			\end{itemize}
		\end{itemize}
	}
\end{frame}

>>>>

\section{Algorithm}
\subsection{Deterministic component}
\begin{frame}{Deterministic component}
	\Wider{
		\begin{itemize}
			\item  \textbf{Setup:}
			\begin{itemize}
				\item  For each pair of orbitals $\left\{p,q\right\}$, store a list of %triplets
				$\left\{r,s,\left|H\left(rs\leftarrow pq\right)\right|\right\}$,
				sorted by $\left|H\left(rs\leftarrow pq\right)\right|$ in decreasing order
				\item Also compute (for sampling algorithm):
				\begin{eqnarray}
				\sum_{rs\in\textrm{remaining}} |H(rs\leftarrow pq)|
				\end{eqnarray}
			\end{itemize}
			{\color{white}  skip line}
			\\
			\uncover<2->{
				\item \textbf{Finding important connected determinants} $D_j$ (for which $\left|H_{ji}\right|>\epsilon$): %for at least one $i\in \mathcal{V}$)
				\\{\color{white}  skip line}
				\\
			}
			\begin{itemize}
				\uncover<3->{
					%\item  \textbf{Generate only those double excitations that exceed $\epsilon$.}
					%\\
					\item For each pair of occupied orbitals $\left\{p,q\right\}$, look up the stored list
					of triplets $\left\{r,s,\left|H\left(rs\leftarrow pq\right)\right|\right\}$ and iterate
					through the list until a triplet is reached for which $\left|H\left(rs\leftarrow pq\right)\right|<\epsilon$
				}
				\\{\color{white}  skip line}
				\\
			\end{itemize}
		\end{itemize}
	}
\end{frame}
